A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

\begin{abstract}
%\boldmath
Traditionally, a central server is used to provide support to MMGs (massively multiplayer games), where the number of participants is in the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, in order to minimize the maintenance cost of its infra-structure, but critical questions remain. Examples of the problems relative to peer-to-peer MMG support systems are: vulnerability to cheating, overload of the upload links of the peers and difficulty to maintain consistency of the simulation among the participants. In this work, it is proposed the utilization of geographically distributed lower-cost nodes, working as a distributed server to the game. The distribution model and some related works are also presented. To address the communication cost imposed to the servers, we specify a novell refinement to the area of interest technique, significantly reducing the necessary bandwidth. Simulations have been made with ns-2, comparing different area of interest algorithms. The results show that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.

@@

Usually, the network support for this kind of application consists in a central server with plenty of resources (processing power and available bandwidth), which accepts connections from the clients. Each player interacts through one of these clients, which sends his actions to the server, that processes them, calculating their influence over the game, and broadcasts the action's result to every client. Due to the number of simultaneous participants that this kind of game usually has, these tasks demand for a significant amount of resources from the server, which receives and processes the actions from all the players and broadcast state updates to every one of them.

Nos últimos anos, têm-se pesquisado alternativas à abordagem com servidor centralizado. Uma delas é a distribuição, entre os próprios participantes, tanto da simulação do jogo quanto da responsabilidade de atualizarem-se entre si quando realizam ações. A comunicação entre eles ocorre par-a-par, formando uma rede descentralizada \cite{schiele2007rpp}. Esta abordagem seria o ideal, não fossem alguns problemas que lhe são inerentes. Por exemplo, como os jogadores participam do processamento da simulação, é necessário que eles entrem em acordo no que diz respeito ao estado da partida, sob pena de haver inconsistências caso isto não seja feito.

Outra questão se refere ao número de envios que cada participante tem que executar. No modelo cliente-servidor, basta que cada um envie suas ações para o servidor, que se encarrega de simular e difundir o novo estado para os outros jogadores. No caso do modelo par-a-par, cada par envolvido torna-se responsável por processar suas ações e enviar as atualizações de estado para os outros participantes. O problema disto reside no fato de que não se pode garantir que todos os jogadores possuam conexões de rede com largura de banda suficiente. Por fim, sem um servidor central, que poderia atuar como árbitro, o jogo torna-se dependente da simulação que os próprios jogadores executam, que pode ser desvirtuada de forma a chegar a um resultado inválido, que beneficie indevidamente determinado jogador ou mesmo que invalide a sessão de jogo.

Além do modelo par-a-par, existe também a alternativa de utilizar um servidor distribuído, em que diversos nodos conectados entre si dividem a tarefa de simular o jogo, como também de enviar as atualizações de estado aos jogadores \cite{assiotis2006dam}. Tal abordagem possibilita o uso de computadores de menor custo para comporem o sistema distribuído servidor, barateando a infra-estrutura de suporte. Questões como consistência e vulnerabilidade a trapaça podem ser abstraídas, restringindo o conjunto de nodos servidores a computadores comprovadamente confiáveis, o que é plausível, levando em conta que o número de nodos servidores deverá ser algumas ordens de grandeza menor do que o número de jogadores. Além disso, não é necessário exigir que cada jogador envie atualizações de estado para todos os outros jogadores. Com menores exigências de largura de banda e processamento das máquinas clientes, o jogo torna-se acessível para um maior público.
%Tendo em vista a dificuldade de criar um modelo de suporte par-a-par que ao mesmo tempo garanta consistência, resistência a trapaça e eficiência de comunicação, o modelo de servidor distribuído foi escolhido como objeto deste trabalho.

%Alguns trabalhos [citações] têm proposto técnicas para reduzir a carga de processamento e comunicação associada a servidores de jogos maciçamente multijogador, sendo uma alternativa a distribuição desta carga entre diversos servidores, cada um com custo de aquisição e manutenção menor do que o de um grande servidor central. Ainda assim, com as atuais técnicas de distribuição e modelo de comunicação entre os servidores e os clientes, têm-se um alto custo para manter o sistema servidor distribuído como um todo.
No entanto, para evitar que o custo de manutenção do sistema distribuído servidor como um todo não se aproxime do custo de manutenção de um servidor central, é necessário realizar algumas otimizações com o intuito de reduzir a largura de banda necessária para cada um dos nodos. O presente trabalho propõe uma técnica para reduzir o consumo de largura de banda causado pelo tráfego do jogo entre os servidores e os clientes, diminuindo a quantidade de recursos necessários, através de um refinamento da técnica de gerenciamento de interesse \cite{boulanger2006cim} dos jogadores. O princípio básico desta técnica é que cada participante do jogo receba apenas atualizações de jogadores cujo estado lhes seja relevante. Foram realizadas simulações comparando a proposta deste trabalho com técnicas convencionais, obtendo resultados significativos. %Além disso, propõe-se uma técnica que visa prover qualidade de serviço, adaptando a freqüência de atualizações enviadas pelo servidor à disponibilidade de recursos. [sure?]Outra consiste em um heurística para detecção de aglomerados de jogadores - ou hotspots - de forma a otimizar o balanceamento de carga entre os servidores.[/sure?]

>>>>

\begin{abstract}
%\boldmath
Traditionally, a central server is utilized to provide support to MMGs (massively multiplayer games), where the number of participants is in the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, in order to minimize the maintenance cost of its infrastructure, but critical questions remain. Examples of the problems relative to peer-to-peer MMG support systems are: vulnerability to cheating, overload of the upload links of the peers and difficulty to maintain consistency of the simulation among the participants. In this work, it is proposed the utilization of geographically distributed lower-cost nodes, working as a distributed server to the game. The distribution model and some related works are also presented. To address the communication cost imposed to the servers, we specify a novell refinement to the area of interest technique, significantly reducing the necessary bandwidth. Simulations have been made with ns-2, comparing different area of interest algorithms. The results show that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.

@@

Usually, the network support for this kind of application consists in a central server with plenty of resources (processing power and available bandwidth), which accepts connections from the clients. Each player interacts through one of these clients, which sends his actions to the server, that processes them, calculating their influence over the game, and broadcasts the action's result to every client. Due to the number of simultaneous participants that this kind of game usually has, these tasks demand a significant amount of resources from the server, which receives and processes the actions from all the players and broadcast state updates to all of them.

Recently, some alternatives to the central server approach have been researched. One of them is to distribute among the own participants the game simulation and the task to broadcast the state updates when they perform actions. Communication between them is in a peer-to-peer manner, forming a decentralized network \cite{schiele2007rpp}. This approach would be the ideal if it did not have not some critical inherent drawbacks. For example, as the player computers participate on the simulation, they need to agree on the resulting state of the game match. If this agreement does not happen, some inconsistency on the game state among the players may occur.

There is another question, concerning the number of trasmissions that each peer needs to execute. In the client-server model, each client only needs to send his actions to the server, which processes them and broadcasts the resulting game state to every player. In the peer-to-peer model, each peer becomes responsible for processing its own player's actions and send the resulting state to everyone else to whom that state change might be relevant. The problem is that we cannot assume that every client has enough bandwidth to do this. Besides, without a central server, the game becomes dependant of the peers' simulation, which can be corrupted in order to result in an invalid state which benefits a player, or even invalidate the whole game session.

Besides the peer-to-peer model, another alternative is to use a distributed server, in which nodes connected between them divide the game simulation and the state update broadcasts \cite{assiotis2006dam}. Such approach allows for the use of lower-cost computers to form the distributed server system, reducing the cost of the support infrastructure. Also, consistency maintenance becomes easier than with the peer-to-peer model, because a single server decides the simulation for its assigned portion of the world, and problems related to malicious players may be abstracted, since the servers are able to verify the simulation and detect cheating. Finally, with less bandwidth and processing power requirements for the clients, the game becomes accessible for a wider public.

%Alguns trabalhos [citações] têm proposto técnicas para reduzir a carga de processamento e comunicação associada a servidores de jogos maciçamente multijogador, sendo uma alternativa a distribuição desta carga entre diversos servidores, cada um com custo de aquisição e manutenção menor do que o de um grande servidor central. Ainda assim, com as atuais técnicas de distribuição e modelo de comunicação entre os servidores e os clientes, têm-se um alto custo para manter o sistema servidor distribuído como um todo.
However, to avoid the distributed server system maintenance cost to be the same as the central server's, it is necessary to perform some optimizations, in order to reduce the necessary bandwidth for each server node. The present work proposes an algorithm to reduce the bandwidth usage caused by the game traffic between servers and clients, through a refinement of the players' interest management technique \cite{boulanger2006cim}.

No entanto, para evitar que o custo de manutenção do sistema distribuído servidor como um todo não se aproxime do custo de manutenção de um servidor central, é necessário realizar algumas otimizações com o intuito de reduzir a largura de banda necessária para cada um dos nodos. O presente trabalho propõe uma técnica para reduzir o consumo de largura de banda causado pelo tráfego do jogo entre os servidores e os clientes, diminuindo a quantidade de recursos necessários, através de um refinamento da técnica de gerenciamento de interesse \cite{boulanger2006cim} dos jogadores. O princípio básico desta técnica é que cada participante do jogo receba apenas atualizações de jogadores cujo estado lhes seja relevante. Foram realizadas simulações comparando a proposta deste trabalho com técnicas convencionais, obtendo resultados significativos. %Além disso, propõe-se uma técnica que visa prover qualidade de serviço, adaptando a freqüência de atualizações enviadas pelo servidor à disponibilidade de recursos. [sure?]Outra consiste em um heurística para detecção de aglomerados de jogadores - ou hotspots - de forma a otimizar o balanceamento de carga entre os servidores.[/sure?]
